---
title: "homework-4"
author: "Riley Maher"
date: "12/2/2020"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Homework 4

## Importing Packages

```{r}
library(ggplot2)
library(tidyverse)
library(gender)
library(leaflet)
library(udpipe)
library(textrank)

model <- udpipe_download_model(language = "english")
```

## Reading Data

```{r}
# Reading in and cleaning the data
airbnb <- read.csv('Modified_AB_NYC_2019.csv')
airbnb$id <- NULL
airbnb$X <- NULL
airbnb$reviews_per_month <- ifelse(is.na(airbnb$reviews_per_month) == TRUE, 0,
                                   airbnb$reviews_per_month)

head(airbnb)
```

## Data Structure and Summary

```{r}
# Structure of the data
str(airbnb)
```

```{r}
# Summary of the data
summary(airbnb)
```

## Initial Data Analysis

### Room Type Breakdown

```{r}
# Barplot of types of airbnbs
home_split <- ggplot(airbnb, aes(x=room_type)) + geom_bar()
home_split
```

```{r}
# Average price by room type
price_per_airbnb_type <- round(tapply(airbnb$price,
                                      airbnb$room_type, mean, na.rm=TRUE), 2)
price_per_airbnb_type
```

```{r}
# Average number of reviews by room type
reviews_per_airbnb_type <- tapply(airbnb$reviews_per_month,
                                   airbnb$room_type, mean, na.rm=TRUE)
reviews_per_airbnb_type
```

### Borough Type Breakdown

```{r}
# Number of airbnbs by borough type
borough_split <- ggplot(data = airbnb, aes(x = neighbourhood_group)) + geom_bar()
borough_split
```

```{r}
# Number of airbnbs in the cities in the largest borough in NYC
airbnb %>%
  filter(neighbourhood_group == "Manhattan") %>%
  ggplot(aes(x=neighbourhood)) + geom_bar() + theme(axis.text.x = element_text(angle = 90))

```

```{r}
# Average price per neighborhood group
price_per_neighborhood <- round(tapply(airbnb$price,
                                      airbnb$neighbourhood_group, mean, na.rm=TRUE), 2)
price_per_neighborhood
```

## Exploratory Data Analysis

### Minimum Nights by Price

```{r}
# Scatterplot of price by minimum night
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x = minimum_nights, y = price)) + geom_point() + geom_smooth()

```

### Price by Gender

```{r}
# I used this loop to get the genders of all the names. It took a super long time so I created a new CSV with it. I left it here commented out to show you.# airbnb$gender <- "other"

# airbnb$gender <- "other"
# num <- 1
# 
# for(i in airbnb$host_name) {
#   if (nrow(gender(i)['gender']) == 0) {
#     airbnb$gender[num] <- "other"
#   }
#   else if (gender(i)['gender'] == "male"){
#     airbnb$gender[num] <- "male"
#   }
#   else {
#     airbnb$gender[num] <- "female"
#   }
#   print(num)
#   num <- num + 1
# }
# 
# write.csv(airbnb, file = "Modified_AB_NYC_2019.csv")

# Calculating the average rental price by borough
price_per_gender <- sort(round(tapply(airbnb$price, airbnb$gender, mean, na.rm=TRUE), 2))
price_per_gender

# Calculatiing the average rental rate by gender
barplot(price_per_gender)

```

### Rental Rates by Borough

```{r}
# Calculating the average rental rate by borough
rental_rates <- sort(round(tapply(airbnb$price, airbnb$neighbourhood_group, mean, na.rm=TRUE), 2))
rental_rates

# Plotting the rental rates by borough
barplot(rental_rates)
```

### Review Importance

```{r}
# Scatterplot of reviews per airbnb less than $1000
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x = number_of_reviews, y = price, alpha = .35)) + geom_point() + geom_smooth()

```

### Description Effect on Price

#### Length of Description on Price

```{r}
# Counting the number of words in each description
airbnb$name_length <- 0
num <- 1

for(i in airbnb$name){
  airbnb$name_length[num] <- sapply(strsplit(i, " "), length)
  num <- num + 1
}

name_length_price <- slice(airbnb, name_length, price)

# Scatterplot that shows description length vs. price
name_length_price %>%
  filter(price < 1000) %>%
  ggplot(aes(x = name_length, y = price, alpha = .35)) + geom_point()
```

#### Frequency of Key Words on Price

```{r}
# I used this block to create a CSV with the most frequent words. I stored it in a CSV because it took pretty long to run. I also had to exclude a few words because the annotation did not accurately classify their part of speech.

# udmodel <- udpipe_load_model(model$file_model)
# 
# desc <- udpipe_annotate(udmodel, airbnb$name)
# desc <- data.frame(desc)
# 
# keyw <- textrank_keywords(desc$lemma,
#                           relevant = desc$upos %in% c("NOUN", "VERB", "ADJ"))
# sub_key <- filter(subset(keyw$keywords, ngram == 1 & freq > 1),
#                   keyword != 'in',
#                   keyword != 'with',
#                   keyword != 'near')
# sub_key
# write.csv(sub_key, file = "Word_Freq.csv")
```

```{r}
# Load in frequency CSV and get top 10 words for all descriptions
word_freq <- read.csv('Word_Freq.csv')
word_freq$X <- NULL
word_freq <- slice(word_freq, 1:10)

# Bar graph of top 10 most frequent words
word_freq %>%
  ggplot(aes(x = keyword, y = freq)) +
  geom_bar(stat='identity') +
  theme(axis.text.x = element_text(angle = -60))
```
```{r}

# Creating vectors to assign to new dataframe columns
for (i in 1:10){
  assign(paste("vec", i, sep = ""), grepl(word_freq$keyword[i], airbnb$name))
}

# Assigning vectors to different columns -- this could be more efficient, but I can't figure it out
airbnb$room <- vec1
airbnb$heart <- vec2
airbnb$apartment <- vec3
airbnb$bedroom <- vec4
airbnb$cozy <- vec5
airbnb$spacious <- vec6
airbnb$Manhattan <- vec7
airbnb$min <- vec8
airbnb$sunny <- vec9
airbnb$close <- vec10

# Room vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=room, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'room' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Heart vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=heart, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'heart' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Apartment vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=apartment, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'apartment' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Bedroom vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=bedroom, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'bedroom' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Cozy vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=cozy, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'cozy' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Spacious vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=spacious, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'spacious' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Manhattan vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=Manhattan, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'Manhattan' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Min vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=min, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'min' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Sunny vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=sunny, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'sunny' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)

# Close vs. Price Boxplot
airbnb %>%
  filter(price < 1000) %>%
  ggplot(aes(x=close, y=price)) +
  geom_boxplot() +
  labs(title="Keyword 'close' Affect on Price", x="Keyword Included", y="Price ($)") +
  stat_summary(fun=mean, geom="point", shape=23, size=4)
```


```{r}
# Wrote more CSVs to once again speed up the process

# # Creating the top and bottom 1000 priced airbnbs
# ordered_bnb <- airbnb[order(-airbnb$price),]
# top_1000 <- slice(select(ordered_bnb, name), 1:1000)
# bottom_1000 <- slice(select(ordered_bnb, name), 48895:47895)
# 
# # Finding the most frequent words for the top 1000 priced airbnbs
# desc_top <- udpipe_annotate(udmodel, top_1000$name)
# desc_top <- data.frame(desc_top)
# 
# keyw_top <- textrank_keywords(desc_top$lemma,
#                           relevant = desc_top$upos %in% c("NOUN", "VERB", "ADJ"))
# sub_key_top <- filter(subset(keyw_top$keywords, ngram == 1 & freq > 1),
#                   keyword != 'in',
#                   keyword != 'with',
#                   keyword != 'near')
# 
# # Finding the most frequent words for the bottom 1000 priced airbnbs
# desc_bottom <- udpipe_annotate(udmodel, bottom_1000$name)
# desc_bottom <- data.frame(desc_bottom)
# 
# keyw_bottom <- textrank_keywords(desc_bottom$lemma,
#                           relevant = desc_bottom$upos %in% c("NOUN", "VERB", "ADJ"))
# sub_key_bottom <- filter(subset(keyw_bottom$keywords, ngram == 1 & freq > 1),
#                   keyword != 'in',
#                   keyword != 'with',
#                   keyword != 'near')
# 
# # Writing CSVs for the top and bottom 1000 priced frequent words
# write.csv(sub_key_top, file = "Top_Word_Freq.csv")
# write.csv(sub_key_bottom, file = "Bottom_Word_Freq.csv")
```

```{r}
# Load in frequency CSV and get top 10 words for top 1000 descriptions
top_word_freq <- read.csv('Top_Word_Freq.csv')
top_word_freq$X <- NULL
top_word_freq <- slice(top_word_freq, 1:10)

# Bar graph of top 10 frequent words in top 1000 priced airbnbs
top_word_freq %>%
  ggplot(aes(x = keyword, y = freq)) +
  geom_bar(stat='identity') +
  theme(axis.text.x = element_text(angle = -60))
```



```{r}
# Load in frequency CSV and get top 10 words for bottom 1000 descriptions
bottom_word_freq <- read.csv('Bottom_Word_Freq.csv')
bottom_word_freq$X <- NULL
bottom_word_freq <- slice(bottom_word_freq, 1:10)

# Bar graph of top 10 frequent words in bottom 1000 priced airbnbs
bottom_word_freq %>%
  ggplot(aes(x = keyword, y = freq)) +
  geom_bar(stat='identity') +
  theme(axis.text.x = element_text(angle = -60))
```

## Expensive Rentals on a Map

```{r}
lat_long_price <- airbnb[order(-airbnb$price),]
lat_long_price <- slice(select(lat_long_price, latitude, longitude, price), 1:100)

leaflet() %>% 
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>% 
  addCircles(data = lat_long_price, weight = 5)
```

